Plots for \enquote{Arrows for Parallel Computations}

### 2018-01-03 paper/separate_plots/main.tex
scaling done

\meanOverheadPlot{Mean Overhead for distributed \\ \rmtest 44497 256}{0.02}{32}{272}{\benchmarkDir/distributed-rm/44497-256-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 3217}{0.5}{32}{272}{\benchmarkDir/distributed-jacobi/3-4253-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 4253}{0.5}{32}{272}{\benchmarkDir/distributed-jacobi/3-4253-diff.csv}

@@

\speedupplot{Speedup of distributed \jacobitest \enquote{3217}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-jacobi/bench-jacobi.bench.jacobi-parr-3-4253.csv};
}{272}{\plotwidthDist}{272}

\speedupplot{Speedup of distributed \jacobitest \enquote{4253}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-jacobi/bench-jacobi.bench.jacobi-parr-3-4253.csv};
}{272}{\plotwidthDist}{272}

@@

\meanOverheadPlot{Mean Overhead for distributed \\ \torustest 4096}{0.5}{32}{272}{\benchmarkDir/distributed-torus/4096-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs Eden CP}{0.5}{4}{18}{\benchmarkDir/sm-rm/eden-cp-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs Eden CP}{0.5}{4}{18}{\benchmarkDir/sm-rm/eden-cp-11213-64-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs GpH}{0.5}{4}{18}{\benchmarkDir/sm-rm/mult-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs GpH}{0.5}{4}{18}{\benchmarkDir/sm-rm/mult-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs Par Monad}{0.5}{4}{18}{\benchmarkDir/sm-rm/par-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs Par Monad}{0.5}{4}{18}{\benchmarkDir/sm-rm/par-11213-32-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \sudokutest 1000 vs Eden CP}{0.5}{4}{18}{\benchmarkDir/sudoku-sm/eden-cp-1000-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \sudokutest 1000 vs GpH}{0.5}{4}{18}{\benchmarkDir/sudoku-sm/mult-1000-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \sudokutest 1000 vs Par Monad}{0.5}{4}{18}{\benchmarkDir/sudoku-sm/par-1000-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \torustest 512 vs Eden CP}{0.5}{4}{18}{\benchmarkDir/torus-sm/eden-cp-512-diff.csv}

>>>>

\meanOverheadPlot{Mean Overhead for distributed \\ \rmtest 44497 256}{0.04}{32}{272}{\benchmarkDir/distributed-rm/44497-256-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for distributed \\ \jacobitest 3217}{0.04}{32}{272}{\benchmarkDir/distributed-jacobi/3-3217-diff.csv}

@@

\speedupplot{Speedup of distributed \jacobitest \enquote{3217}}{PArrows Eden}{256}{32}{
\addplot+ [very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{\benchmarkDir/distributed-jacobi/bench-jacobi.bench.jacobi-parr-3-3217.csv};
}{272}{\plotwidthDist}{32}

@@

\meanOverheadPlot{Mean Overhead for distributed \\ \torustest 4096}{0.04}{32}{272}{\benchmarkDir/distributed-torus/4096-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs Eden CP}{0.04}{4}{18}{\benchmarkDir/sm-rm/eden-cp-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs Eden CP}{0.03}{4}{18}{\benchmarkDir/sm-rm/eden-cp-11213-64-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs GpH}{0.2}{4}{18}{\benchmarkDir/sm-rm/mult-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs GpH}{0.05}{4}{18}{\benchmarkDir/sm-rm/mult-11213-64-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 32 vs Par Monad}{0.2}{4}{18}{\benchmarkDir/sm-rm/par-11213-32-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \rmtest 11213 64 vs Par Monad}{0.2}{4}{18}{\benchmarkDir/sm-rm/par-11213-64-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \sudokutest 1000 vs Eden CP}{0.05}{4}{18}{\benchmarkDir/sudoku-sm/eden-cp-1000-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \sudokutest 1000 vs GpH}{0.05}{4}{18}{\benchmarkDir/sudoku-sm/mult-1000-diff.csv}
\\
\meanOverheadPlot{Mean Overhead for shared-memory \\ \sudokutest 1000 vs Par Monad}{0.05}{4}{18}{\benchmarkDir/sudoku-sm/par-1000-diff.csv}

@@

\meanOverheadPlot{Mean Overhead for shared-memory \\ \torustest 512 vs Eden CP}{0.05}{4}{18}{\benchmarkDir/torus-sm/eden-cp-512-diff.csv}
